---
title: "patchwork_cheat_sheet"
author: "Hanjuan Zhang"
date: "3/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package used

```{r,warning=FALSE,message=FALSE}
library(ggplot2)
library(patchwork)
library(magick)
library(png)
```

## Install and Load the Packages

```{r}
#install.packages('patchwork')

# grab the development version from github using devtools
#install.packages("devtools")
#devtools::install_github("thomasp85/patchwork") 
```

## Plot Assembly
```{r}
p1 <- ggplot(mtcars) + 
  geom_point(aes(mpg, disp)) + 
  ggtitle('Plot 1')

p2 <- ggplot(mtcars) + 
  geom_boxplot(aes(gear, disp, group = gear)) + 
  ggtitle('Plot 2')

p3 <- ggplot(mtcars) + 
  geom_point(aes(hp, wt, colour = mpg)) + 
  ggtitle('Plot 3')

p4 <- ggplot(mtcars) + 
  geom_bar(aes(gear)) + 
  facet_wrap(~cyl) + 
  ggtitle('Plot 4')
```

### + 
Using + to add plots together
```{r}
p1 + p2
```

### /
/ will stack the plots together.
```{r}
p1/p2
```

### |
| place the plots beside each other.
```{r}
p3 | (p1 / p2)
```

### plot_spacer()
create an empty area in between plots
```{r}
p1 + plot_spacer() + p2 
```


### Adding plots to the patchwork

```{r}
p1 + grid::textGrob('Some really important text')
wrap_elements(grid::textGrob('Text on left side')) + p1
p1 + gridExtra::tableGrob(mtcars[1:10, c('mpg', 'disp')])
```

## Controlling Layout

### plot_layout()
controll the order of the layout.

```{r}
p1 + p2 + p3 + p4 + 
  plot_layout(ncol = 3)
p1 + p2 + p3 + p4 + 
  plot_layout(widths = c(2, 1))
p1 + p2 + p3 + p4 + 
  plot_layout(widths = c(2, 1), heights = unit(c(5, 1), c('cm', 'null')))

layout <- "
##BBBB
AACCDD
##CCDD
"
p1 + p2 + p3 + p4 + 
  plot_layout(design = layout)
```

### inset_element() 
```{r}
p1 + inset_element(p2, left = 0, bottom = 0.6, right = 0.4, top = 1, align_to = 'full')

p1 + inset_element(
  p2, 
  left = 0.5, 
  bottom = 0.5, 
  right = unit(1, 'npc') - unit(1, 'cm'), 
  top = unit(1, 'npc') - unit(1, 'cm')
)
```


## Annotating
title, subtitle, caption
tag_levels
tag_prefix, tag_suffix
theme

```{r}
(p1 | (p2 / p3)) + 
  plot_annotation(title = 'The surprising story about mtcars')
```
